Concurrent semantics for left-linear rewriting [in adhesive categories]

### 2025-02-20 domains/domains.tex
minori

\begin{proposition}\label{prop:abstoswitch}
	Let $(\der{D, \alpha, \omega})$ and $(\der{D}', \alpha, \omega')$ be two derivation with an abstract equivalence among them with the identity as first component. Then $\id{n}$ is a semi-consistent permutation among them.
\end{proposition}
\begin{proof}
Let $\xi\colon \tpro{D}\to \lpro \der{D}'\rpro$ be the arrow induced by 
\[\xi \circ \iota_{G_i}:=\iota'_{G'_i}\circ \phi_{G_i}\] 
Then we have
	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha} & G_0 \ar[dl]^{\id{G_0}} \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi}\\ G_0 \ar[rr]_{\iota'_{G_0}} & &\lpro \der{D}' \rpro\\L_i \ar[r]^{m_i} \ar[d]_{m'_{i}}& G_i \ar[dl]^{\phi_i} \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi} & R_i \ar[r]^{h_i} \ar[d]_{h'_{i}}& G_{i+1} \ar[dl]_{\phi_{i+1}} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{i}}}&& \lpro \der{D}' \rpro& G'_{i+1} \ar[rr]_{\iota'_{G'_{i+1}}}&& \lpro \der{D}' \rpro}\]
\end{proof}

@@

	Since

>>>>

\begin{proposition}\label{prop:abstoswitch}
	Let $(\der{D, \alpha, \omega})$ and $(\der{D}', \alpha, \omega')$ be two derivation with an abstract equivalence among them with the identity as first component. Then $\id{n}$ is a semi-consistent permutation among them.
\end{proposition}
\begin{proof}
Let $\xi\colon \tpro{D}\to \lpro \der{D}'\rpro$ be the unique arrow $\tpro{D}\to \lpro \der{D}'\rpro$ satisfying 
\[\xi \circ \iota_{G_i}:=\iota'_{G'_i}\circ \phi_{G_i}\]

Then the square below commute.
	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha} & G_0 \ar[dl]^{\id{G_0}} \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi}\\ G_0 \ar[rr]_{\iota'_{G_0}} & &\lpro \der{D}' \rpro\\L_i \ar[r]^{m_i} \ar[d]_{m'_{i}}& G_i \ar[dl]^{\phi_i} \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi} & R_i \ar[r]^{h_i} \ar[d]_{h'_{i}}& G_{i+1} \ar[dl]_{\phi_{i+1}} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{i}}}&& \lpro \der{D}' \rpro& G'_{i+1} \ar[rr]_{\iota'_{G'_{i+1}}}&& \lpro \der{D}' \rpro}\]
	But this is exactly the thesis.
\end{proof}

@@

Now, the sequence of switches between $\lpro \der{D}''\rpro$ and  $\lpro \der{E}'' \rpro$  witnesses that $\id{2}$ is a consistent permutation and so there is a mediating isomorphism $\xi_{\id{2}}$. On the other hand, by
